---
title: "Review_BasicR1"
author: "Jinhee Jaiden Han"
date: '2021 2 2 '
output: html_document
---
# This is a kind of remider for me that I learned so far before the new course begins.

```{r setup}
library(tidyverse)
```

### What was the first I learned? At first, Be careful typos of variables. It seems like small but commonly makes a mistake and the code will not run.

### Basic R markdwon grammar
> A footnote^[this is a footnote]
>
> A horizontal rule<hr />
>
> A block quote<blockquote>This is a block quote.</blockquote>


### Using 'filter()' and 'select()' fucntions

```{r}
mpg #call the data frame
```

### New data frame
* chevrolet's suv and midsize models in 2008
* manufacturer, model, trans, class, cty

```{r}
chevy_mpg <- mpg %>% 
  filter(manufacturer == "chevrolet",
         class %in% c("suv", "midsize"),
         year == "2008") %>% 
  select(manufacturer, model, trans, class, cty)

chevy_mpg
```

### Plotting

```{r}
ggplot(data = chevy_mpg) +
  geom_point(mapping = aes(x = class, y = cty))
```

### Summarizing

```{r}
chevy_mpg %>% 
  group_by(class) %>% 
  summarize(cty_mean = mean(cty)) 
```

